Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2023-08-29 paper.tex
Add files via upload

	To be more specific,

>>>>

	To be more specific, Table~\ref{tab:bertall} shows comparisons of metrics among all competing models backed by $\text{BERT}_{base}$. We can see that our proposed framework, $\text{AUG}$, consistently outperforms all other baselines across multispanQA dataset. Baked by $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 63.05 and 79.42, respectively. Moreover, when equipped with entities' information, $\text{AUG}_{eree}$  achieves even higher EM F1 scores of 63.93 but relatively lower Overlap F1 of 77.50 on the same datasets and encoder.
	These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 1.61 to 2.49 percents across validation datasets. Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 70.35 and 69.15 respectively on the same datasets.These scores represent EM and Overlap F1 improvements of 2.02 and 0.93 compared to the previous setup. Totally the results, shown in Table~\ref{tab:robertaall} demonstrate similar trends to $\text{BERT}_{base}$.
